---
title: "Su_X_HW4"
author: "Xueqi Su"
output: html_document
---
##Prof G - Nice work!
##Prof G - I had to add lines to get output printed to the console.
MATH 510
HW4

1. Create the vectors
```{r}
#(a)
c(1:20)
#(b)
c(20:1)
#(c)
c(1:20,19:1)
#(d)
tem <- c(4,6,3)
#(e)
##use 'times' here to repeat the vectors 10 times.
rep(tem, times = 10)
#(f)
##use 'length.out' here to limit the length of the vectors. Because
##the question asks us to return eleven 4, ten 6, and ten 3, we set
##the length as 11+10+10=31 to get the vectors.
rep(tem, length.out = 31)
#(g)
##we use 'c(10,20,30)' to ask the function repeat 4,6,3 ten, twenty, 
##and thirty times respectively.
rep(tem, c(10,20,30))
```


2.Create a vector	of the values	of e^x*cos(x)	at x = 3,3.1,3.2,...,5.9,6.

```{r}
## we first set up the vector x. Use 'by' function here to indicate 
##the interval between each vectors.
x = seq(3,6,by = 0.1)

##Then we calculate the value of e^x*cos(x)
q2<- exp(x)*cos(x)
q2 ##Prof G - Added this
```

3.Create the following vectors:
```{r}
#(a)
## we first set up vectors q3a1 and q3a2. Use 'by' function here to 
##indicate the interval between each vectors.
q3a1 = seq(3,36,by = 3)
q3a2 = seq(1,34,by = 3)
##calculate the value
q3a3 <- 0.1^q3a1*0.2^q3a2
q3a3 ##Prof G - Added this
#(b)
q3b1 = c(1:25)
q3b2 = (2^q3b1)/q3b1
q3b2 ##Prof G - Added this
```

4.Calculate the	following:
```{r}
#(a)
i = c(10:100)
sum(i^3+4*i^2)
#(b)
i2 = c(1:25)
sum(2^i2/i2+3^i2/i2^2)
```

5.Use the function paste to	create the following character vectors of	
length 30:

```{r}
#(a)
##use 'paste' function here to get we want
paste(rep("lable",30),1:30)
#(b)
##use 'sep=''' to remove the space between the "fn" and numbers.
paste(rep("fn",30),1:30, sep='')
```

6.Execute the following lines which create two vectors of random integers. which are chosen with	replacement	from the integers	0,	1,	.	.	.	,	999. Both	vectors	have length	250.

```{r}

set.seed(50)
## we want to save and restore our numbers for further use.
n = 250
## pick 250 numbers out of [0,999] to form vectors xVec and yVec. And 
##set replace = T here to sampling with replacement.
xVec <- sample(0:999, n, replace=T)
yVec <- sample(0:999, n, replace=T)

#(a)
##use [-1] here to remove the first number of vector yVec; use [-n] 
##to remove the 250th number of xVec.
yVec[-1]-xVec[-n]

#(b)
sin(yVec[c(1:n-1)])/cos(xVec[c(2:n)])

#(c)
##use [-index] here to remove the number on the index positions we 
##indicate.
xVec[c(-250:-249)]+2*xVec[c(-1,-250)]-xVec[c(-2:-1)]

#(d)
sum(exp(-xVec[-1])/(xVec[-250]+10))


```

7.This question	uses the vectors xVec	and	yVec created in	the previous question	and	the	functions	sort, order, mean, sqrt, sum and abs.

```{r}
#(a)
yVec[yVec>600]
#(b)
##use 'which' to get the index positions.
which(yVec>600)
#(c)
xVec[which(yVec>600)]
#(d)
##use 'abs' to get the absolute value.
sqrt(abs(xVec-mean(xVec)))
#(e)
##use 'length' to get the number of values the vector has.
length(yVec[yVec>max(yVec)-200])
#(f)
##use '%%' to calculate the mod. Since we want to know which xVec is 
##divisible by 2, we want the mod to be 0 when we divide xVec by 2.
length(xVec[xVec%%2==0])
#(g)
##we order yVec first, and then use the order of yVec to sort the 
##numbers in xVec.
xVec[order(yVec)]
#(h)
##since we want the values in yVec at index positions 1, 4, 7,...the 
##interval between each index is 3. We use (T,F,F) here to ask the 
##function to keep the first value and give up the 2nd and 3rd values 
##in every three-value-strings.
yVec[c(T,F,F)]
```

8.By using the function	cumprod	or otherwise,	calculate:
```{r}
##use 'cumprod' to get what we want.
##Prof G - This needs to be explained a bit more.
1+sum(cumprod(seq(2,38, by = 2)/(seq(3,39, by = 2))))
```

